\documentclass[12pt, letterpaper]{article}
\usepackage{problems}
\title{\emph{To Mock A Mockingbird} Reading Group\\Week 1 Problems}
\begin{document}
\maketitle

\disclaimer

\begin{prob}{9.1}
$A$ is fond of $x$ when $Ax = x$. If 1) for any two birds $A$ and $B$ there is a bird $C$ such that for any bird $x$, $Cx = A(Bx)$ and 2) the forest contains a mockingbird $Mx = xx$, then must every bird be fond of at least one bird? Or is there at least one bird which is not fond of any bird?
\end{prob}

\begin{prob}{9.2}
A bird is \emph{egocentric} if it is fond of itself. Prove that if the conditions of 9.1 hold then at least one bird is egocentric.
\end{prob}

\begin{prob}{9.3}
$A$ and $B$ \emph{agree} on $x$ if $Ax = Bx$. A bird $A$ is \emph{agreeable} if for every bird $B$, there is at least one bird on which $A$ and $B$ agree. Prove whether condition 1) of 9.1 and the existence of an agreeable bird $A$ guarantee every bird is fond of at least one bird. (Bonus: Why is 9.1 a special case of 9.3? Hint: Is a mockingbird necessarily agreeable?)
\end{prob}

\begin{prob}{9.4}
Suppose condition 1) of 9.1 holds and that $A$, $B$, and $C$ are birds such that $C$ composes A with B. Prove that if $C$ is agreeable then $A$ is also agreeable.
\end{prob}

\begin{prob}{9.5}
Suppose condition 1) of 9.1 holds. Prove that for any birds $A$, $B$, and $C$ there is a bird $D$ such that for every bird $x$, $Dx = A(B(Cx))$.
\end{prob}

\begin{prob}{9.6}
$A$ and $B$ are \emph{compatible} if there is a bird $x$ and a bird $y$ such that $Ax = y$ and $By = x$. Prove that if the conditions of 9.1 hold, then any two birds are compatible.
\end{prob}

\begin{prob}{9.7}
A bird is \emph{happy} if it is compatible with itself. Prove that any bird that is fond of at least one bird must be happy.
\end{prob}

\begin{prob}{9.8}
A bird is \emph{normal} if it is fond of at least one bird. Prove that if condition 1) of 9.1 holds and there is at least one happy bird, then there is at least one normal bird.
\end{prob}

\end{document}
