\documentclass[12pt, letterpaper]{article}
\usepackage{problems}
\title{\emph{To Mock A Mockingbird} Reading Group\\Week 8 Problems}
\begin{document}
\maketitle
\setcounter{section}{13}

\disclaimer

\begin{prob}{13.1}   
Derive $\Theta$ from $B$, $M$, and $R$ using five letters.
\end{prob}

\begin{prob}{13.2}   
Derive $\Theta$ from $B$, $M$, and $C$ using five letters.
\end{prob}

\begin{prob}{13.3}   
Derive $\Theta$ bird from $M$, $B$, and $L$.
\end{prob}

\begin{prob}{13.4}   
Derive $\Theta$ from $M$, $B$, and $W$.
\end{prob}

\begin{prob}{13.5}   
Derive $\Theta$ from $B$, $C$, and $W$. (Note: Solve 13.6 first.)
\end{prob}

\begin{prob}{13.6}   
Derive $\Theta$ from $Q$, $L$, and $W$.
\end{prob}

\begin{prob}{13.7}   
Now solve 13.5.
\end{prob}

\begin{prob}{13.8}   
Derive $\Theta$ from only $Q$ and $M$.
\end{prob}

\begin{prob}{13.9}   
Derive $\Theta$ from $S$ and $L$.
\end{prob}

\begin{prob}{13.10}  
Derive $\Theta$ from $B$, $W$, and $S$ using five letters.
\end{prob}

\begin{prob}{13.11}  
Derive a Turing bird $Uxy = y(xxy)$ from $B$, $M$, and $T$. (Note: You may use any bird derivable from $B$, $M$, and $T$.)
\end{prob}

\begin{prob}{13.12}  
Derive $\Theta$ from $U$ alone.
\end{prob}

\begin{prob}{13.13}  
Derive an owl $Oxy = y(xy)$ from $Q$ and $W$ alone.
\end{prob}

\begin{prob}{13.14}  
Derive $U$ from $O$ and $L$.
\end{prob}

\begin{prob}{13.15}  
Derive $M$ from $O$ and $I$.
\end{prob}

\begin{prob}{13.16}  
Derive $O$ from $S$ and $I$.
\end{prob}

\begin{prob}{13.17}  
Prove that if $x$ is fond of $y$, then x is also fond of $xy$.
\end{prob}

\begin{prob}{13.18}  
Prove that $O\Theta$ is a sage bird.
\end{prob}

\begin{prob}{13.19}  
Prove that $\Theta O$ is a sage bird.
\end{prob}

\begin{prob}{13.20}  
Prove that an owl is fond only of sage birds.
\end{prob}

\begin{prob}{13.21}  
A bird is \emph{choosy} if it is fond only of sage birds. Prove that if $A$ is choosy then $\Theta A$ is a sage bird.
\end{prob}

\begin{prob}{13.22}  
Birds $A_1$ and $A_2$ are \emph{similar} if for all birds $x$, $A_1x = A_2x$. Prove that $O\Theta$ is similar to $\Theta$.
\end{prob}

\begin{prob}{13.23}  
A forest is extensional if no two distinct birds are similar. Prove that in an extensional forest, an owl is fond of all sage birds.
\end{prob}

\end{document}
