\documentclass[12pt, letterpaper]{article}
\usepackage{problems}
\title{\emph{To Mock A Mockingbird} Reading Group\\Week 11 Problems}
\begin{document}
\maketitle

\disclaimer

\begin{prob}{21.1}  
How do you find a bird $Ay = yA(AyA)$?
\end{prob}

\begin{prob}{21.2}  
What about $Ayz = z(yA)(yAz)$?
\end{prob}

\begin{prob}{21.E1} 
Try both methods explained in this chapter to find a sage bird $Ax = x(Ax)$.
\end{prob}

\begin{prob}{21.E2} 
Using both methods, find a bird $Ax = xA$. (Chief Bird Mocker's Note: The solution to this exercise in the book contains an error.)
\end{prob}

\begin{prob}{21.E3} 
Use the first method to find: a) $Ax = Axx$, b) $Ax = A(xx)$, and c) $Ax = AA(xx)$.
\end{prob}

\begin{prob}{21.E4} 
Find a bird $Ax = AA$.
\end{prob}

\begin{prob}{21.E5} 
Find a) $Axy = xyA$, b) $Axy = Ayx$, and c) $Axy = x(Ay)$.
\end{prob}

\begin{prob}{21.E6} 
Use the fact that there must be a bird $Axab = x(Aaab)(Abab)$ to prove that for any birds $a$ and $b$ there are birds $c$ and $d$ such that $acd = c$ and $bcd = d$.
\end{prob}

\begin{prob}{22.1}  
Prove that in a forest with at least two birds, a kestrel cannot be fond of an identity bird.
\end{prob}

\begin{prob}{22.2}  
Under the same assumption, prove that no bird is both a kestrel and an identity bird.
\end{prob}

\begin{prob}{22.3}  
Now prove no starling can be fond of a kestrel.
\end{prob}

\begin{prob}{22.4}  
Prove that no starling is also an identity bird.
\end{prob}

\begin{prob}{22.5}  
Could a bird be both a starling and a kestrel? (Chief Bird Mocker's Note: The provided solution to this problem relies on the assumption that this forest contains an identity bird. Why is this assumption justified?)
\end{prob}

\begin{prob}{22.6}  
Prove that $Kx \neq K$ for any bird $x$. (Hint: Recall that if $Kx = Ky$, then $x = y$.)
\end{prob}

\begin{prob}{22.7}  
Prove $Kx \neq I$.
\end{prob}

\begin{prob}{22.8}  
Prove that no bird can be both a kestrel and a thrush.
\end{prob}

\begin{prob}{22.9}  
Prove no thrush can be egocentric.
\end{prob}

\begin{prob}{22.10} 
Prove that $RII \neq I$. (Note: You could also try proving $RI \neq I$ and $R \neq I$.)
\end{prob}

\begin{prob}{22.11-13} 
Prove no robin, cardinal, or vireo can be egocentric.
\end{prob}

\begin{prob}{22.14} 
Prove that a) no warbler is fond of an identity bird and b) no warbler is egocentric.
\end{prob}

\begin{prob}{22.15}
Prove that a) $SI$ is not fond of $I$ and b) no starling is egocentric. (Note: You can also show no starling is fond of an identity bird.) (Chief Bird Mocker's Note: The solution to this problem in the book contains an error.)
\end{prob}

\begin{prob}{22.16} 
Prove that a) $BKK \neq KK$ and b) no bluebird is egocentric.
\end{prob}

\begin{prob}{22.17} 
Can a queer bird be egocentric?
\end{prob}

\begin{prob}{22.18} 
Explain why constructing the series $K$, $KK$, $KKK$, $KKKK$,... doesn't prove there are infinitely many birds in the forest.
\end{prob}

\begin{prob}{22.19}
Let $K_1 = K$ and $K_{n+1}$ = $KK_n$. Step 1: Show that if $n > 1$ then $K_n \neq K$. Step 2: Show that if $K_{n+1} = K_{m+1}$ then $K_n = K_m$. Step 3: Use the previous steps to prove that if $n \neq m$ then $K_n \neq K_m$.
\end{prob}

\begin{prob}{23.1}
Let $t = K$ and $f = KI$. Find a bird $N$ such that $Nt = f$ and $Nf = t$.
\end{prob}

\begin{prob}{23.2-5}
A bird $x$ is \emph{propositional} when $x = t$ or $x = f$. Let $p$ and $q$ be propositional. Find $c$, $d$, $i$, and $e$ such that $cpq = p \wedge q$, $dpq = d \vee q$, $ipq = i \to q$, and $epq = p \leftrightarrow q$.
\end{prob}

\end{document}
