\documentclass[12pt, letterpaper]{article}
\usepackage{problems}
\title{\emph{To Mock A Mockingbird} Reading Group\\Week 4 Problems}
\begin{document}
\maketitle

\disclaimer

\begin{prob}{9.20}
Suppose a forest contains an agreeable identity bird $Ix = x$. Must every bird be normal? (Note: We are not given the conditions of 9.1.)
\end{prob}

\begin{prob}{9.21}
Suppose there is an identity bird $I$ and that every bird is normal. Does it follow that $I$ is agreeable?
\end{prob}

\begin{prob}{9.22}
Suppose there is an identity bird $I$ and that every pair of birds is compatible. Which of the following conclusions can be validly drawn? 1. Every bird is normal. 2. $I$ is agreeable.
\end{prob}

\begin{prob}{9.23}
If there were a hopelessly egocentric identity bird, the situation would be quite sad. Why?
\end{prob}

\begin{prob}{9.24}
Prove that if a forest contains a lark $Lxy = x(yy)$ and an identity bird then it must also contain a mockingbird.
\end{prob}

\begin{prob}{9.25}
Prove that if a forest contains a lark, then every bird is normal. (Chief Bird Mocker's Note: Remember this proof for later.)
\end{prob}

\begin{prob}{9.26}
Why is a hopelessly egocentric lark unusually attractive?
\end{prob}

\begin{prob}{9.27}
Assuming that no bird can be both a lark and a kestrel, prove that no lark is fond of a kestrel.
\end{prob}

\begin{prob}{9.28}
Prove that if a kestrel is fond of a lark then every bird is fond of the lark.
\end{prob}

\begin{prob}{9.29}
Derive an expression for an egocentric bird only in terms of a lark $L$ using twelve letters.
\end{prob}

\begin{prob}{10.1}
A bird $\Theta$ is a \emph{sage bird} if for any bird $x$, $x$ is fond of $\Theta x$. Prove that if the conditions of 9.1 hold and there exists a bird $A$ such that $A$'s response to any bird $x$ is a bird that composes $x$ with $M$, that the forest contains a sage bird.
\end{prob}

\end{document}
